% !TeX root = ../thesis.tex

\begin{acknowledgements}
  Firstly, I would like to express my deepest gratitude to my advisor, Anonymous, for his guidance and support during my PhD study. Reflecting on 2021, I feel incredibly fortunate to have been introduced to the concept of ``chiplet,'' a groundbreaking topic at the time. Thanks to Anonymous’s mentorship, I had the privilege of accessing cutting-edge technologies and tackling some of the most critical challenges in the field of integrated circuits, keeping my research at the forefront of industry advancements.
  
  I would like to express my sincere gratitude to Prof. Dong Xiang for his invaluable guidance on network architecture. I was fortunate to take his High-Performance Interconnection Networking course, where I systematically learned the fundamentals of interconnection and routing theory. I would like to extend my sincere gratitude to Prof. Torsten Hoefler for guiding me in transitioning from single-node computer architecture to the broader realm of supercomputer and datacenter architecture. I would like to thank Prof. Mingyu Gao. I was fortunate to take his Computer Architecture course, where I gained a solid foundation in the fundamental principles and essential skills of architecture. 

  I would like to thank my fellow members at Archip Lab, as well as my collaborators at SPCL and Intel. Their support, insights, and camaraderie have been invaluable throughout my research journey. I want to express my special thanks to Yuchen Wei, whose expertise in algorithms and programming has been an incredible asset. I am also deeply grateful to Zhanhong Tan, Jingwei Cai, Guiming Shi, Zehua Li, Yijie Guan, Siyuan Shen, Tianchen Chen, Shiju Wang, and many others for their valuable assistance and insightful discussions, all of which have significantly contributed to the progress of my research.

  I would like to thank José Duato, Brian Towles, John Kim, William Dally, and many other researchers, whose seminal works and insightful publications have profoundly influenced and enriched my research. This thesis stands as a testament to the inspiration I have drawn from their groundbreaking contributions to the field.

  I would like to express my gratitude to my wife, Chun Ning, for her support and encouragement. Her patience, understanding, and belief in me have been a constant source of strength, especially during the most challenging moments of my research. I would also like to express my deepest gratitude to my parents. I know that they will always be my strongest supporters, standing by my side through every challenge and success.

\end{acknowledgements}
